\begin{thebibliography}{A}

% Konferenzbeitrag

\bibitem[Agrawal, Konolige \& Blas 2008]{AKB08}
	M.~Agrawl, K.~Konolige and M.~Blas: {\em CenSurE: Center Surround Extremas for Realtime Feature Detection and Matching}.
	\newblock in Computer Vision-ECCV 2008, pp.102-115, Springer Berlin/Heidelberg
	
\bibitem[ARToolKit]{ART}
	ARToolKit http://www.hitl.washington.edu/artoolkit/ 
	Zuletzt besucht: 02.12.2011
	
\bibitem[Arun, Huang \& Blostein 1987]{AHB87}
    K.S.~Arun, T.S.~Huang and S.D.~Blostein: {\em Least-squares fitting of two 3-D point sets}. 
    \newblock IEEE Trans Pattern Anal Machine Intell (1987) 9:698?700.
  
\bibitem[Besl \& McKay 1992]{BM92}  
    P.~Besl and N.~McKay: {\em A Method for Registration of 3-D Shapes}. 
    \newblock Trans. PAMI, Vol. 14, No. 2, 1992.
    
\bibitem[Black \& Yacoob 1997]{BY97}
    M.J.~Black and Y.~Yacoob: {\em Recognizing Facial Expressions in Image Sequences Using Local Parameterized Models of Image Motion}
    \newblock International Journal of Computer Vision 25(1), 23-48 (1997)

\bibitem[Chavarria \& Sommer 2007]{CS07}
	M.A.~Chavarria and G.~Sommer: {\em Structural ICP algorithm for pose estimation based on local features}.
	\newblock Computer Vision Theory and Applications - VISAPP , pp. 341-346, 2007

\bibitem[Chen \& Medioni 1991]{CM91}
	Y.~Chen, G.~Medioni: {\em Object Modeling by Registration of Multiple Range Images}.
	\newblock Proc. IEEE Conf. on Robotics and Automation, 1991.
	
\bibitem[Conte et al. 2004]{C04}
	D.~Conte, P.~Foggia, C.~Sansone and M.~Vento: {\em Thirty years of graph matching in pattern recognition}.
	\newblock International Journal of Pattern Recognition and Artificial Intelligence Vol. 18, No. 3 (2004) 265-298
	
\bibitem[Cordella et al. 2004]{CF04}
	L.P.~Cordella, P.~Foggia, C.~Sansone and M.~Vento: {\em A (Sub)Graph Isomorphism Algorithm for Matching Large Graphs}.
	\newblock IEEE TRANSACTIONS ON PATTERN ANALYSIS AND MACHINE INTELLIGENCE, VOL. 26, NO. 10, OCTOBER 2004
    
\bibitem[DBSCAN Wiki]{DWiki}
	DBSCAN Wikipedia: http://de.wikipedia.org/wiki/DBSCAN
	Zuletzt besucht: 11.05.2012
	
\bibitem[Dorai, Weng \& Jain 1997]{DMJ97}
	C.~Dorai, J.~Weng and A.K.~Jain: {\em Optimal registration of object views using range data}.
	\newblock IEEE Transactions on Pattern Analysis and Machine Intelligence. 19(10):1131-1137, 1997
	
\bibitem[Eggert, Lorusso \& Fisher 1997]{ELF97}
	D.W.~Eggert, A.~Lorusso, R.B.~Fisher: {\em Estimating 3-D rigid body transformations: a comparison
of four major algorithms}.
	\newblock Machine Vision and Applications (1997) 9: 272-290.
	
\bibitem[Eppstein 1999]{E99}
	D.~Eppstein: {\em Subgraph Isomorphism in Planar Graphs and Related Problems}.
	\newblock Journal of Graph Algorithms and Applications, vol. 3, no. 3, pp. 1?27 (1999)
	
\bibitem[Ester et.al 1996]{E96}
	M.~Ester, H.P.~Kriegel, J.~Sander and X.~Xu: {\em A Density-Based Algorithm for Discovering Clusters in Large Spatial Databases with Noise}.
	\newblock Knowledge Discovery and Data Mining. Seite 226-231, 1996
		
\bibitem[Haag \& Nagel 1999]{HN99}
	M.~Haag and H.~Nagel: {\em Combination of Edge Element and Optical Flow Estimates for 3D-Model-Based Vehicle Tracking in Traffic Image Sequences}.
	\newblock  International Journal of Computer Vision, Volume 35, Number 3, 295-319, 1999
	
\bibitem[Harris 1992]{H92}
	C.~Harris: {\em Tracking with Rigid Objects}. 
	\newblock MIT Press. 1992
	
\bibitem[Horn \& Schunck 1981]{HS81}
	B.K.P.~Horn and B.G.~Schunck: {\em Determining optical flow}.
	\newblock Artificial Intelligence Volume 17, Issues 1?3, August 1981, Pages 185-203


\bibitem[Horn 1987]{H87}
	B.K.P.~Horn: {\em Closed-form solution of absolute orientation using unitquaternions}. 
	\newblock J. Opt. Soc. Am. A, vol. 4, 629-642, 1987. 
	
\bibitem[ICP Wiki]{IW}
	ICP Wikipedia http://de.wikipedia.org/wiki/Iterative\_ Closest\_ Point\_ Algorithm
	Zuletzt besucht: 02.02.2012
	
\bibitem[Josiger \& Kirchner 2003]{JK03}
	M.~Josiger and K.~Kirchner: {\em Moderne Clusteralgorithmen - eine vergleichende Analyse auf zweidimensionalen Daten}.
	\newblock Proc. FGML Workshop (FGML 2003), S.80-84, Karlsruhe 2003
	 
\bibitem[Jurie \& Dhome 2001]{JD01}
	F.~Jurie and M.~Dhome: {\em A simple and efficient template matching algorithm}.
	\newblock  International Conference on Computer Vision (ICCV 01) 2 (2001) 544-549.
	
\bibitem[Kinect]{KIN}
	Kinect http://www.xbox.com/en-US/kinect 
	Zuletzt besucht: 02.12.2011
	
\bibitem[Kinect-How it works]{KINH}
	Kinect-How it works
	\newblock http://www.cadet.at/wp-content/uploads/2011/02/kinect\_ tech.pdf
	Zuletzt besucht: 15.03.2012
	
\bibitem[Kanatani 1994]{K94}
	K.~Kanatani: {\em Analysis of 3-D rotation fitting}. 
	\newblock IEEE Trans Pattern Anal Machine Intell (1994) 16:543-549
	
\bibitem[Karypis et.al 1999]{K99}
	G.~Karypis, E.U.~Han and V.~Kumar: {\em CHAMELEON: A Hierarchical Clustering Algorithm Using Dynamic Modeling}.
	\newblock IEEE Computer, 32:8, S.68-75, 1999
	
\bibitem[Lamdan et al. 1988]{LSW88}
	Y.~Lamdan, J.T.~Schwatrtz and H.J.~Wolfson: {\em On recognition of 3-D objects from 2-D images}.
	\newblock In Proceedings of IEEE International Conference on Robotics and Automation, 1988

\bibitem[Lepetit \& Fua 2005]{LF05}
	V.~Lepetit and P.~Fua: {\em Monocular Model-Based 3D Tracking of Rigid Objects: A Survey}.
	\newblock Foundations and Trends in Computer Graphics and Vision Vol.1, No 1(2005) 1-89.

\bibitem[Lucas \& Kanade 1981]{LK81}
	B.D.~Lucas and T.~Kanade: {\em An Iterative Image Registration Technique with an Application to Stereo Vision}.
	\newblock Proceedings of Imaging Understanding Workshop, pp. 121-130 (1981).
	
\bibitem[Messmer \& Bunke 1998]{MB98}
	B.T.~Messmer and H.~Bunke: {\em A New Algorithm for Error-Tolerant Subgraph Isomorphism Detection}.
	\newblock IEEE TRANSACTIONS ON PATTERN ANALYSIS AND MACHINE INTELLIGENCE, VOL. 20, NO. 5, MAY 1998
	
\bibitem[Mills \& Novins 2000]{MN00}
	S.~Mills and K.~Novins: {\em Motion Segmentation in Long Image Sequences}. 
	\newblock In Proceedings of the British Machine Vision Conference 2000, pp.162-171.
	
\bibitem[Odessa 2011]{O11}
	Odessa 
	\newblock http://computer-vision-talks.com/2011/01/comparison-of-the-opencvs-feature-detection-algorithms-2/ 
	Zuletzt besucht: 02.12.2011
	
\bibitem[PMD CamCube Einführung]{pmde}
	PMDs CamCube Einführung: http://www.pmdtec.com/fileadmin/pmdtec/downloads/documentation/datenblatt\_ camcube3.pdf
	Zuletzt besucht: 13.03.2012
	
\bibitem[PMD CamCube Entwicklungstutor]{pmdd}
	PMDs CamCube Development Tutorial: http://www.pmdtec.com/fileadmin/pmdtec/downloads/documentation/camcube\_ softwaredevelopmenttutorial.pdf
	Zuletzt besucht: 14.03.2012
	
\bibitem[Rhijn \& Mulder 2005]{AJ05}
	A.~van Rhijn and J.~D.~Mulder: {\em Optical Tracking and Calibration of Tangible Interaction Devices}.
	\newblock IPT \& EGVE Workshop, 2005.
	
\bibitem[Rusinkiewicz \& Levoy 2001]{RL01}
	S.~Rusinkiewicz and M.~Levoy: {\em Efficient Variants of the ICP Algorithm}.
	\newblock In Proceeding of the Third Intl. Conf. on 3D Digital Imaging and Modeling, pages 145-152, Quebec City, Canada

\bibitem[Scott \& Longuet-Higgins 1991]{SL91}
	G.L.~Scott and H.C.~Longuet-Higgins: {\em An algorithm for associating the features of two images}.
	\newblock In Proc. Royal Society London, 1991, vol.B244, pp.21-26.

\bibitem[Shi \& Tomasi 1994]{ST94}
	J.~Shi and C.~Tomasi: {\em Good features to track}.
	\newblock in IEEE Computer Society Conference: Computer Vision and Pattern Recognition, 1994. 

\bibitem[TOF-Kamera Wikipedia]{TOFWiki}
	TOF-Kamera Wikipedia: http://de.wikipedia.org/wiki/Time-of-flight-Sensor
	Zuletzt besucht: 02.04.2012

\bibitem[Tomasi \& Kanade]{TK91}
	C.~Tomasi and T.~Kanade: {\em Detection and Tracking of Point Features}.
	\newblock CiteSeerX - Scientific Literature Digital Library and Search Engine (United States)
	
\bibitem[Ullmann 1976]{U76}	
	J.R.~Ullmann: {\em An Algorithm for Subgraph Isomorphism}.
	\newblock Journal of the ACM (JACM), Volume 23 Issue 1, Jan. 1976 

\bibitem[Umeyama 1991]{U91}
	S.~Umeyama: {\em Least-squares estimation of transformation parameters between two point patterns}. 
	\newblock IEEE Trans Pattern Anal Machine Intell (1991) 13:376?380

\bibitem[Vaccetti, Lepetit \& Fua 2004]{VLF04}
	L.~Vacchetti, V.~Lepetit and P.~Fua: {\em Combining edge and texture information for real-time accurate 3D camera tracking}.
	\newblock Proceedings of the Third IEEE and ACM International Symposium on Mixed and Augmented Reality, 2004 
	
\bibitem[VICON]{VIC}
	http://www.vicon.com 
	Zuletzt besucht: 01.12.2011

\bibitem[Zhang et.al 1996]{Z96}
	T.~Zhang, R.~Ramakrishnan and M.~Livny: {\em BIRCH: An efficient data clustering method for very large databases}. 
	\newblock Proceedings of the 1996 ACM SIGMOD International Conference on Management of Data, Montnreal, 1996, S.103-144
	
\bibitem[Zhang \& Navab 2000]{ZN00}
	X.~Zhang and N.~Navab: {\em Tracking and pose estimation for computer assisted localization in industrial environments}. 
	\newblock Applications of Computer Vision, 2000, Fifth IEEE Workshop on.
	
\bibitem[Zhang et al. 1995]{Z95}
	Z.~Zhang, R.~Deriche, O.~Faugeras and Q.~Luong: {\em A robust technique for matching two uncalibrated images through the recovery of the unknown epipolar geometry}.
	\newblock Artificial Intelligence Volume 78, Issues 1?2, October 1995, Pages 87-119



\end{thebibliography}
